Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-17 papers/B1555_EdgeOn/B1555_letter.tex
Minor format changes

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, little perturbations in the gravitational potential are sufficient to bring flux ratio anomalies in strong lensed systems. 
Moreover, unlike in the optical or infrared, in the radio band, lensed images are not sensitive to micro lensing from stars nor dust extinction. 
This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}. While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure. An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}. Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are
  expected to deliver new large samples of gravitationally lensed
  quasar, in the near future the discovery of new systems using
narrow-line quasar emission \citep{N14} will provide new
  invaluable statistical perspective on current constraints based on
  flux ratio anomalies.  In this paper, we explore the alternative
  idea that flux ratio anomalies are not related to the presence of
  substructure but originate in a more complex lens galaxy mass
  distribution than initially considered. To this end we use new
  infra-red data from the Strong lensing at High Angular Resolution
  Program(SHARP). The main goal of the SHARP project is to
  re-observe known quadruple and Einstein ring lens systems at a much
higher angular resolution by making use of the Keck adaptive optics
(AO) telescope and large interferometric arrays \citep{SHARP12,V12}
. In particular, to better understand the cause of flux ratio
anomalies in strong lens systems we focus on the lens
  modelling of the lens system B1555+375 (included in both the
  observational and theoretical analysis of \citet{Dalal2002} and
  \citet{Xu14}, respectively) by making use of the new information
obtained from the latest SHARP infrared imaging. The paper is
  organized as follows: the latest SHARP data is introduced in section
  2; in section 3 we present the lens model while the results of this
  analysis and their implication are discussed in section 4.

@@

\begin{figure*}
\begin{minipage}{140mm}
\includegraphics[width=140mm]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.}
%
\end{minipage}

>>>>

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems.
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05,V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are expected to
deliver new large samples of gravitationally lensed quasars, in the
near future the discovery of new systems using narrow-line quasar
emission \citep{N14} will provide new invaluable statistical
perspective on current constraints based on flux ratio anomalies.  In
this paper, we explore the alternative idea that flux ratio anomalies
are not related to the presence of substructure but originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program(SHARP). The main goal of
the SHARP project is to re-observe known quadruple and Einstein ring
lens systems at a much higher angular resolution by making use of the
Keck adaptive optics (AO) telescope and large interferometric arrays
\citep{SHARP12,V12} . In particular, to better understand the cause of
flux ratio anomalies in strong lens systems we focus on the lens
modelling of the lens system B1555+375 (included in both the
observational and theoretical analysis of \citet{Dalal2002} and
\citet{Xu14}, respectively) by making use of the new information
obtained from the latest SHARP infrared imaging. The paper is
organized as follows: the latest SHARP data is introduced in section
2; in section 3 we present the lens model while the results of this
analysis and their implication are discussed in section 4.

@@

\begin{figure*}
%\begin{minipage}{140mm}
%\includegraphics[width=140mm]{B1555_gallery.eps}
\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.}
%
%\end{minipage}
